---
output: 
  github_document:
    pandoc_args: --webtex=http://chart.apis.google.com/chart?cht=tx&chl=
bibliography: dependencies.bib   
---

<!--  use the --webtex argument in the YAML to render equations -->

```{r, include = FALSE}
knitr::opts_chunk$set(
  collapse = TRUE,
  comment = "#>",
  fig.path = "man/figures/README-",
  out.width = "100%",
  warning = FALSE, 
  results = "asis",
  encoding ='UTF-8'
)
```


<!-- badges: start -->

<!-- badges: end -->


```{r echo=FALSE, message=FALSE}
# following code for loading and writing the bibtex references for the used 
# packages is adapted from the blog post: //www.r-bloggers.com/bibliography-with-knitr-cite-your-references-and-packages/,
# by Michael


# required packages
packages <- c("tidyverse",    # plotting, data-wrangling
              "gridExtra",    # multiplot
              "marelac",      # geochemical database plug-in
              "readxl",       # reading xls workbooks
              "gtable",       # multiplot
              "bibtex",       # writing bibtex files
              "grid",         # drawing
              "knitr",        # for knitting rmarkdown files
              "png",          # read and write bitmap images
              "sp",           # spatial data
              "rgdal",        # geospatial data
              "rgeos",        # geometry engine
              "lattice",      # graphing 
              "RColorBrewer", # color palletes
              "Cairo",        # for per mille sign rendering in figures
              "rmarkdown"     # rmarkdown
              )    


# load packages
invisible(lapply(packages, library, character.only = TRUE))

# get the packages version 
packages_versions <- function(p) {
  paste(packageDescription(p)$Package, packageDescription(p)$Version, sep = " ")
}

# get the R reference
rref <- citation()

# create ref key
rref$key <- "rversion"

# write the R reference
write.bib(rref, "rversion.bib")

# get the packages references
write.bib(packages, "packages.bib")

# merge the R reference and the packages references
cat(paste("% Automatically generated", Sys.time()), "\n% DO NOT EDIT",
    { readLines("rversion.bib") %>% 
      paste(collapse = "\n") },
    { readLines("packages.bib") %>% 
      paste(collapse = "\n") },
    file = "dependencies.bib",
    sep = "\n")

file.remove("packages.bib", "rversion.bib") %>% 
  invisible()

```

# Introduction
To recreate the article: *A nutrient control on marine anoxia during the end-Permian mass extinction*, published in *Nature Geoscience*, run the R Markdown files (.Rmd) with *knitr* [@knitr1; @knitr2; @knitr3; @rmarkdown1; @rmarkdown2] on the programming platform R [@rversion].  Instructions on the installation and the usage of Rmarkdown for Rstudio can be found on the website: https://rmarkdown.rstudio.com/. Several additional packages are required to recreate data processing, statistics and visualization of the geochemical datasets and geographic maps, including:*bibtex* [@bibtex], *Cairo* [@Cairo], *gtable* [@gtable], *gridExtra* [@gridExtra], *png* [@png], *lattice* [@lattice], RColorBrewer [@RColorBrewer],  *readxl* [@readxl], *rgdal* [@rgdal], *rgeos* [@rgeos], *sp* [@sp1; @sp2], and *tidyverse* [@tidyverse]. The library *marelac* [@marelac] was used for chemical data transformations. Complete the pathway to approriate directory on lines 6, 7 and 78 of *Schobbenetal_main.Rmd* and lines 6, 7 and 82 of *Schobbenetal_SI.Rmd* before rendering the files[^r_version].

# Structure

The structure of this repository is as follows:

- **data-raw**: contains the raw data files
- **datafiles**: contains proccesed data files
- **style**: contains templates for formatting


[^r_version]: `r version$version.string`, with: `r paste(lapply(sort(packages), packages_versions), collapse = ", ")`.

# References
